Covariant Phase Space via MultiSymplectic Geometry

### 2017-05-31 cpsviams.tex
Implemented corrections by MS.

\title{Covariant Phase Space via MultiSymplectic Geometry}
\author{
	International Ph.D. Program in "Science" \\
	"Differential geometry and applications to modern physics" \\
	Department of Mathematics and Physics\\
	Università Cattolica del Sacro Cuore\\
	via Musei X, Brescia xxx, \underline{Italy}
}

@@

\begin{abstract}
In this short talk we present the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
In particular we focus our attention on the construction of the \emph{Covariant Phase Space} starting from the multi-symplectic approach to geometric classic field theories.
%Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.

@@

\section{Multisymplectic landscape at glance}
Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.

\begin{center}
  \includestandalone[mode=buildnew]{Pictures/Figure_ms_landscape}
\end{center}

\begin{itemize}
 \item the starting point is the \emph{configuration bundle} 
 	\begin{displaymath}
 		E = \left( \pi_{M,E} : E\rightarrow M \right)
 	\end{displaymath}
 	the object encoding the kinematics.
 \item from that we have constructed the \emph{I jet bundle} applying the jet functor to $E$ 
 	\begin{displaymath}
 	J^1E = \left( \pi_{J^1 M,E} : J^1 E\rightarrow E \right)
 	\end{displaymath} 
 	that is an affine bundle over $E$.
 \item then, we considered other two vector bundle derived from the first jet bundle. 
 	The twisted affine dual of $J^1E$ 
 	\begin{displaymath}
 	\AffDualJet  = \left( \pi_{ \AffDualJet ,E} : \AffDualJet  \rightarrow E \right)
 	\end{displaymath}
 	called \emph{"extended multiphase space"} and th twisted linear dual of $J^1 E$
	\begin{displaymath}
		\LinDualJet  = \left( \pi_{ \LinDualJet ,E} : \LinDualJet \rightarrow E \right)
	\end{displaymath}
	called \emph{"standard multiphase space"} \footnote{$\LinDualJet$ can be seen as the dual bundle of the vector bundle $\vec{J^1E}$ linear model of $J^1E$}.\\
	The first one can be also seen as an affine line bundle over the second one.

\item It turns out that  $\LinDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived by a multicanonical m-form $\theta$, obtained by pulling back the tautological m-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
	Thus, it can be considered the theoretical analogue of the cotangent bundle in ordinary geometric mechanics.

\item Dynamics can be implemented in two different way by fixing a further structure.\\
	In the Lagrangian picture has to be fixed a bundle map:
	\begin{displaymath}
		\Lagrangian : J^1 E \rightarrow \bigwedge^m (M)
	\end{displaymath}
	, called \emph{Lagrangian density}, 	while in the Hamiltonian framework has to be fixed a section:
	\begin{displaymath}
		\Hamiltonian : \LinDualJet \rightarrow \AffDualJet
	\end{displaymath}
	called \emph{Hamiltonian density}.

\item Both of them determine a \emph{Legendre map}, computed as a fiber derivative, which allows us to move from one framework to another.
	Mainly we are interested  in the following:
	\begin{displaymath}
		\mathbb{F} \Lagrangian : J^1 E \rightarrow \AffDualJet		
	\end{displaymath}
	The two dynamics function $\Lagrangian$ and $\Hamiltonian$ can be considered equivalent under the condition of \emph{hyper-regularity}\cite[chapter, p.~215]{Gimmsy}.

\item Via $\mathbb{F} \Lagrangian$ we can pull-back the canonical forms on $J^1 E$ to give the \emph{Poincaré - Cartan forms} giving:
	\begin{displaymath}
		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta 
		\qquad 
		\omega_\Lagrangian = - \diff \theta_\Lagrangian
	\end{displaymath}
	Via $\Hamiltonian$ we can pull-back the canonical forms on $\LinDualJet$ to give the \emph{De Donder - Weyl forms} giving:
	\begin{displaymath}
		\theta_\Hamiltonian = \Hamiltonian^\ast \theta 
		\qquad 
		\omega_\Hamiltonian = - \diff \theta_\Lagrangian
	\end{displaymath}

\item At last, can be introduced two map in order to encoded the field equations.
	In the Lagrangian framework we consider the \emph{Euler-Lagrange map}
	\begin{displaymath}
		D_\Lagrangian : J^2 E \rightarrow V^\TwistedLinear E
	\end{displaymath}
	 a bundle-morphism acting on holonomic section submanifolds $\varphi(M)$ as:
	\begin{displaymath}
		\left\langle D_\Lagrangian(\varphi, \partial \varphi , \partial^2 \varphi) \right\vert \left. V \right\rangle = (j^1 \varphi)^\ast \left( j^1V \lrcorner \omega_\Lagrangian \right)
	\end{displaymath}
	 a bundle-morphism when evaluated on a vertical field $V$ on $E$.\\
	In the Hamiltonian framework we consider the \emph{DeDonder-Weyl map}
	\begin{displaymath}
		D_\Hamiltonian : J^1\left(\LinDualJet \right) \rightarrow V^\TwistedLinear \left(\LinDualJet \right)
	\end{displaymath}
	acting on holonomic section submanifolds $(\varphi, \pi)(M)$ as:
	\begin{displaymath}
		\left\langle D_\Hamiltonian(\varphi, \pi, \partial \varphi , \partial \pi) \right\vert \left. V \right\rangle = (\varphi, \pi)^\ast \left( V \lrcorner \omega_\Hamiltonian \right)
	\end{displaymath}	
	when evaluated on a vertical field $V$ on $\LinDualJet$.

\item	
	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-know motion equations when represented in local coordinate charts.

@@

The smooth bundle to be considered depends on the dynamical framework we are employing.
We introduce the following notation, in order to treat both formalism at the same time:
\begin{notation}
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			 & Lagrangian picture & Hamiltonian picture \\
			\hline
			$F$		&	$E$		&	$\LinDualJet$	\\
			$\downarrow$ & $\downarrow$ & $\downarrow$ \\
			$M$ & $M$ & $M$ \\
			    & \emph{configuration bundle} & \emph{multiphase bundle} \\
			\hline
		\end{tabular}
	\end{center}
\end{notation}

@@

	\begin{definition}[Space of kinematics (off-shell) configurations]\label{Def:ConfSpace}
		Is the, generally non-linear, infinte-dimensional manifold :
		\begin{displaymath}
			\Conf \coloneqq \Gamma^\infty(F,M)
		\end{displaymath}
	\end{definition}
%
	\begin{remark}
		The jet functor $j^1$ acts injectively on smooth cross sections
		\begin{displaymath}
			\Conf \simeq j^k \Gamma^\infty(F)
		\end{displaymath}
		so, we can equivalently consider holonomic jet sections of any order as the element of the configuration space.
	\end{remark}	
%
	\begin{definition}[Space of Dynamics (on-shell) configurations]\label{Def:SolSpace}
		Is the subset of $\Conf$:
		\begin{displaymath}
			\Sol \coloneqq \ker(D_\cdot) \subset \Conf
		\end{displaymath}
		containing all the smooth solutions of the motion equations corresponding to the  dynamical operator $D_\Lagrangian$ or $D_\Hamiltonian$ depending on the framework considered.
	\end{definition}

The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the section of a suitable vector bundle composing with the jet functor $j$.
%
\begin{align*}
	D_\Lagrangian[\; ] &= 
	D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[ \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right) \\
	D_\Hamiltonian[\; ] &= 
	D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[ (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
\end{align*}
%
The target base is a vector space, more precisely a frechet space \cite[Cap.2]{Ban} and makes sense to ask whetever $D_\cdot [\phi]$ is equal to the 0-section.

Again, we would like to employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
\begin{notation}
	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend jet bundle over $F$ of different order, can not be introduced directly a common notation on the multi-symplectic ground but we have to pass to the functional framework:
\begin{displaymath}
	D[\; ] = \; \Gamma^\infty(F) \ni \phi \quad \mapsto \quad D[ \phi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear F \right)\right)
\end{displaymath}	
in other words, $D[\phi](x) \in V^\TwistedLinear_{\phi(x)}F$ is a twisted linear one-form.
\\
	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results:
	\begin{displaymath}
		\left\langle D[\phi] \right\vert \left. V \right\rangle =
		\phi^\ast \left( i_V \omega \right) 
		\begin{cases}
			(j^1 \varphi)^\ast \left( i_{j^1V} \: \omega_\Lagrangian \right) \\
			(\varphi, \pi)^\ast \left( i_V \: \omega_\Hamiltonian \right)
		\end{cases}              
        \in \Omega^m(M)
	\end{displaymath}

	where has been employed the following correspondences:
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			 & Lagrangian picture & Hamiltonian picture \\
			\hline
			$\phi \in \Conf$		&	$j^1 \varphi \; , \quad \varphi \in \Gamma^\infty(E)$		&	$(\varphi, \pi)$	\\
			$V \in \Gamma(\phi^\ast V F )$ & $j^1 V$ & $V$ \\
			$\omega$ & $\omega_\Lagrangian$ & $\omega_\Hamiltonian$ \\
			\hline
		\end{tabular}
	\end{center}	
	%
	Noticing the recurring scheme we will also denote $	W = V^\TwistedLinear F $.
\end{notation}

Remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$. Natural beside the fact that its very structure, as a set, is expicitly determined by the fixed Lagrangian or Hamiltonian.\\
Therefore, is the candidate to  be the field-theoretic (Covariant) phase space.

@@

Since $\Conf$ and $\Sol$ are in general not linear, we have to regard them as a manifold.
Hence, we have to specify conveniently the structure of their tangent space in order to make clear the previous claim.

The first thing to point out is the following chain of inequalities:
\begin{displaymath}
	\Gamma^\infty_c\left(\phi^*(VF)\right) \; \subseteq \; T_\phi\Sol \; \subset \; T_\phi\Conf \; \subseteq \; \Gamma^\infty\left( \phi^\ast (VF) \right)
\end{displaymath}
%
This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
Therefore, a parametrized regular curve as to be regarded as a family of diffeomerphisms, the flow generated by a vertical tangent field on $F$.\\
The pull-back are there to remark that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$ thus are vertical field of $F$ \underline{along} the section $\phi$.
\begin{notation}
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			 & Lagrangian picture & Hamiltonian picture \\
			\hline
			$\delta \phi \in T_\phi \Conf$		&	$\delta \varphi$		&	$(\delta \varphi, \delta \pi)$ \\
			\hline
		\end{tabular}
	\end{center}
\end{notation}

According to this interpretation, $T_\phi\Sol$ should consists of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.\\
In other words, it consists of the solutions of the \emph{Jacobi equations}.
Rigourosly, this can be expressed in the following definition:
	\begin{definition}[Tangent space to the Space of Solutions]\label{Def:TangentSol}
		on a solution $\phi \in \Sol$, is the vector space
		\begin{displaymath}
			T_\phi \Sol \coloneqq \ker(J[\phi]_\cdot)
		\end{displaymath}
		where $J$ is the so-called \emph{Jacobi Operator}.
	\end{definition}

\section{Jacobi Operator}\label{Sec:JacobiOperator}
Intuitively, the Jacobi equation are the formal linearization of the motion equation around a solution $\phi$.\\
Precisely they can be encoded in the following operator:
%
	\begin{definition}[Jacobi operator pertaining to $D$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp} is the bundle map over $F$:
		\begin{displaymath}
			J(\phi) \; : \; \phi^\ast(VF) \rightarrow	\phi^\ast(V^\TwistedLinear F) 
			\quad s.t. \quad  \left(J(\phi)\right) V
			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda](x) \right\rvert_{\lambda=0} \right)
		\end{displaymath}
		where $V\in (\phi^\ast(VF))_{\phi(x)} = V_{\phi(x)}F$ and $\phi_\lambda$ is a regular variation generated by a $\delta\phi$ such that $\delta\phi_x = V$ and
		$\sigma$ is the canonical bundle-morphism \footnote{see \ref{Section:sigma} for further details.}
		\begin{displaymath}
			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
		\end{displaymath}
		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
		 and $0$ is the zero-section of $W$ over $F$.
	\end{definition}
	%
	\begin{remark}
		Being $J$ a bundle morphism, it can be naturally interpreted functionally as
		\begin{displaymath}
			\left(J(\phi)\right) [\: ] : 
			\Gamma^\infty\left(\phi^\ast(VF)\right) \rightarrow	
			\Gamma^\infty \left( 
			\phi^\ast(V^\TwistedLinear F)
			\right)
		\end{displaymath}
	\end{remark}
%
  \begin{minipage}[r]{0.5\textwidth}
    \includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
  \end{minipage}\hfill
  \begin{minipage}[l]{0.5\textwidth}
	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ target on the same space.
  \end{minipage}

@@

\begin{displaymath}
	\left( V_M W \right)_{0(e)} = 
	i\left[ V_E W \right]_{0(e)} \oplus \left( T_e 0 \left[ V_e E\right] \right)
\end{displaymath}
which determine an intrinsic mapping 
\begin{displaymath}
	\sigma_e : \left( V_M W \right)_{0(e)} \rightarrow \left( V_E W \right)_{0(e)} \simeq W_e
\end{displaymath}
that is simply the projection on the first component.

Since we have such projection for all $e \in E$ and it acts fiberwise, it can be regarded as a bundle morphism over $E$:
\begin{displaymath}
	\sigma : 0^\ast \left( V_M W \right) \rightarrow 0^\ast \left( V_E W \right) \simeq W
\end{displaymath} 
Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$.
%

\begin{minipage}{.5\textwidth}
  \centering
	\includestandalone[width=0.85\linewidth, mode=buildnew]{Pictures/Figure_sigmaAction}
 \\ \small{general case}
\end{minipage}
\begin{minipage}{.5\textwidth}
  \centering
	\includestandalone[width=0.85\linewidth, mode=buildnew]{Pictures/Figure_sigmaJacobi}
 \\ \small{ (Jacobi field variation)}
\end{minipage}%

\newpage
\section{Covariant approach: pre-symplectic form}
 Roughly, the strategy of construction is the following:
	\vspace{0.5cm}

  \begin{minipage}[l]{0.5\textwidth}
	\includegraphics[width=\textwidth]{Pictures/symform.png}
  \end{minipage}\hfill
  \begin{minipage}[r]{0.45\textwidth}
	\begin{itemize}
		\item Find a way to contract $\delta \phi$ and $\delta \phi '$ , seen as tangent vector field on $E$, with the multi-symplectic forms $\omega$.
		\item pull-back the obtained $m-1$ form to $M$, oriented manifold.
		\item Integrate thus form on a suitable $(m-1)$ dimensional sub-manifold of $M$.
		\item take the resulting number as the evaluation of the desired form on the two variations.  
	\end{itemize}
  \end{minipage}\hfill

  	\vspace{1cm}

>>>>

\title{Covariant Phase Space via MultiSymplectic Geometry}
\author{
	International Ph.D. Program in "Science" \\
	"Differential geometry and applications to modern physics" \\
	Department of Mathematics and Physics\\
	Universit\'a Cattolica del Sacro Cuore\\
	via Musei 41, 25121 Brescia, \underline{Italy}
}

@@

\begin{abstract}
In this short talk we present the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
In particular we focus our attention on the construction of the \emph{Covariant Phase Space}, starting from the multi-symplectic approach to geometric classic field theories.
%Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.

@@

\section{A glance at the Multisymplectic landscape}
Let us briefly recall the basics of the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.

\begin{center}
  \includestandalone{Pictures/Figure_ms_landscape}
\end{center}

\begin{itemize}
 \item The starting point is the \emph{configuration bundle} 
 	\begin{displaymath}
 		E = \left( \pi_{M,E} : E\rightarrow M \right)
 	\end{displaymath}
 	the object encoding the kinematics.
 \item From that we have constructed the \emph{first jet bundle}, applying the jet functor to $E$ 
 	\begin{displaymath}
 	J^1E = \left( \pi_{J^1 M,E} : J^1 E\rightarrow E \right)
 	\end{displaymath} 
 	which is an affine bundle over $E$.
 \item Then, we considered two other vector bundles derived from the first jet bundle: 
 	the twisted affine dual of $J^1E$ 
 	\begin{displaymath}
 	\AffDualJet  = \left( \pi_{ \AffDualJet ,E} : \AffDualJet  \rightarrow E \right)
 	\end{displaymath}
 	called \emph{"extended multiphase space"} and the twisted linear dual of $J^1 E$
	\begin{displaymath}
		\LinDualJet  = \left( \pi_{ \LinDualJet ,E} : \LinDualJet \rightarrow E \right)
	\end{displaymath}
	called \emph{"standard multiphase space"} \footnote{$\LinDualJet$ can be seen as the dual bundle of the vector bundle $\vec{J^1E}$ linear model of $J^1E$}.\\
	The first one can be also viewed as an affine line bundle over the second one.

\item It turns out that  $\LinDualJet $ carries a naturally defined multi-symplectic form $\omega = -\ExtD \theta$ derived from a multicanonical $m$-form $\theta$, obtained by pulling back the tautological $m$-form $\theta_\Lambda$ from $\bigwedge^m (E)$.\\
	Thus, it can be considered the theoretical analogue of the cotangent bundle in ordinary geometric mechanics.

\item Dynamics can be implemented in two different ways by fixing a further structure.\\
	In the Lagrangian picture one needs to fix a bundle map:
	\begin{displaymath}
		\Lagrangian : J^1 E \rightarrow \wedge^m (M)
	\end{displaymath}
	called \emph{Lagrangian density}, 	while in the Hamiltonian framework we fix a section:
	\begin{displaymath}
		\Hamiltonian : \LinDualJet \rightarrow \AffDualJet
	\end{displaymath}
	called \emph{Hamiltonian density}.

\item Both of them determine a \emph{Legendre map}, computed as a fiber derivative, which allows us to move from one framework to the other.
	Mainly we are interested  in the following:
	\begin{displaymath}
		\mathbb{F} \Lagrangian : J^1 E \rightarrow \AffDualJet		
	\end{displaymath}
	The two dynamical functions $\Lagrangian$ and $\Hamiltonian$ can be considered equivalent under the condition of \emph{hyper-regularity}\cite{Gimmsy}.

\item We can pull-back the canonical forms on $J^1 E$ via $\mathbb{F} \Lagrangian$ to give the \emph{Poincaré - Cartan forms} reading:
	\begin{displaymath}
		\theta_\Lagrangian = \mathbb{F} \Lagrangian^\ast \theta 
		\qquad 
		\omega_\Lagrangian = - \diff \theta_\Lagrangian
	\end{displaymath}
	We can pull-back the canonical forms on $\LinDualJet$ via $\Hamiltonian$ to give the \emph{De Donder - Weyl forms} reading:
	\begin{displaymath}
		\theta_\Hamiltonian = \Hamiltonian^\ast \theta 
		\qquad 
		\omega_\Hamiltonian = - \diff \theta_\Hamiltonian
	\end{displaymath}

\item At last, two map can be introduced in order to encode the field equations.
	In the Lagrangian framework we consider the \emph{Euler-Lagrange map}
	\begin{displaymath}
		D_\Lagrangian : J^2 E \rightarrow V^\TwistedLinear E
	\end{displaymath}
	 which is a bundle-morphism acting along holonomic sections:
	\begin{displaymath}
		\left\langle D_\Lagrangian(\varphi, \partial \varphi , \partial^2 \varphi) \right\vert \left. V \right\rangle = (j^1 \varphi)^\ast \left( j^1V \lrcorner \omega_\Lagrangian \right)
	\end{displaymath}
	 when evaluated on a vertical field $V$ on $E$.\\
	In the Hamiltonian framework we consider the \emph{DeDonder-Weyl map}
	\begin{displaymath}
		D_\Hamiltonian : J^1\left(\LinDualJet \right) \rightarrow V^\TwistedLinear \left(\LinDualJet \right)
	\end{displaymath}
	which is a bundle-morphism acting along holonomic sections:
	\begin{displaymath}
		\left\langle D_\Hamiltonian(\varphi, \pi, \partial \varphi , \partial \pi) \right\vert \left. V \right\rangle = (\varphi, \pi)^\ast \left( V \lrcorner \omega_\Hamiltonian \right)
	\end{displaymath}	
	when evaluated on a vertical field $V$ on $\LinDualJet$.

\item	
	Imposing the vanishing of this map on an holonomic section gives a condition which corresponds to the well-known equations of motion when represented in local coordinate charts.

@@

The smooth bundle to be considered depends on the dynamical framework we are employing.
We introduce the following notation, in order to treat both formalisms at the same time:
\begin{notation}
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			 & Lagrangian picture & Hamiltonian picture \\
			\hline
			$F$		&	$E$		&	$\LinDualJet$	\\
			$\downarrow$ & $\downarrow$ & $\downarrow$ \\
			$M$ & $M$ & $M$ \\
			    & \emph{configuration bundle} & \emph{multiphase bundle} \\
			\hline
		\end{tabular}
	\end{center}
\end{notation}

@@

	\begin{definition}[Space of kinematical (off-shell) configurations]\label{Def:ConfSpace}
		It is the, generally non-linear, infinite-dimensional manifold :
		\begin{displaymath}
			\Conf \coloneqq \Gamma^\infty(F,M)
		\end{displaymath}
	\end{definition}
%
	\begin{remark}
		The jet functor $j^1$ acts injectively on smooth cross sections
		\begin{displaymath}
			\Conf \simeq j^k \Gamma^\infty(F)
		\end{displaymath}
		so, we can equivalently consider holonomic jet sections of any order as elements of the configuration space.
	\end{remark}	
%
	\begin{definition}[Space of Dynamics (on-shell) configurations]\label{Def:SolSpace}
		It is the subset of $\Conf$:
		\begin{displaymath}
			\Sol \coloneqq \ker(D_\cdot) \subset \Conf
		\end{displaymath}
		containing all smooth solutions of equation of motion corresponding to the  dynamical operator $D_\Lagrangian$ or $D_\Hamiltonian$, depending on the framework considered.
	\end{definition}

The key point of the latter definition is that the \emph{Euler-Lagrange} map and the \emph{DeDonder-Weyl} map, being bundle-morphism, can be regarded as mapping from $\Conf$ to the sections of a suitable vector bundle composing with the jet functor $j$.
%
\begin{align*}
	D_\Lagrangian[\; ] &= 
	D_\Lagrangian \circ j^2 : \quad \Gamma^\infty(E) \ni \varphi \quad \mapsto \quad D_\Lagrangian[ \varphi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear E \right)\right) \\
	D_\Hamiltonian[\; ] &= 
	D_\Hamiltonian \circ j^1 : \quad \Gamma^\infty(F) \ni (\varphi,\pi) \quad \mapsto \quad D_\Hamiltonian[ (\varphi,\pi) ] \in \Gamma^\infty \left( (\varphi,\pi)^\ast \left(V^\TwistedLinear F \right)\right)
\end{align*}
%
The target base is a vector space, more precisely a Frechet space \cite[Cap.2]{Ban} and it makes sense to ask whether $D_\cdot [\phi]$ is equal to the 0-section.

Again, we employ a collective notation to denote the motion equation operators $D_\Lagrangian$ and $D_\Hamiltonian$:
%
\begin{notation}
	Since $D_\Lagrangian$ and $D_\Hamiltonian$ depend on jet bundles over $F$ of different orders, a common notation on the multi-symplectic ground cannot be introduced directly
	but we have to pass to the functional framework:
\begin{displaymath}
	D[\; ] = \; \Gamma^\infty(F) \ni \phi \quad \mapsto \quad D[ \phi ] \in \Gamma^\infty \left( \phi^\ast \left(V^\TwistedLinear F \right)\right)
\end{displaymath}	
in other words, $D[\phi](x) \in V^\TwistedLinear_{\phi(x)}F$ is a twisted linear one-form.
\\
	The evaluation of operator $D$, when applied to $\phi$, on a test vector field $V \in \Gamma(\phi^\ast(VF))$, results in:
	\begin{displaymath}
		\left\langle D[\phi] \right\vert \left. V \right\rangle =
		\phi^\ast \left( i_V \omega \right) 
		\begin{cases}
			(j^1 \varphi)^\ast \left( i_{j^1V} \: \omega_\Lagrangian \right) \\
			(\varphi, \pi)^\ast \left( i_V \: \omega_\Hamiltonian \right)
		\end{cases}              
        \in \Omega^m(M)
	\end{displaymath}

	where the following correspondences have been employed:
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			 & Lagrangian picture & Hamiltonian picture \\
			\hline
			$\phi \in \Conf$		&	$j^1 \varphi \; , \quad \varphi \in \Gamma^\infty(E)$		&	$(\varphi, \pi)$	\\
			$V \in \Gamma(\phi^\ast V F )$ & $j^1 V$ & $V$ \\
			$\omega$ & $\omega_\Lagrangian$ & $\omega_\Hamiltonian$ \\
			\hline
		\end{tabular}
	\end{center}	
	%
	For brevity we will also set $	W = V^\TwistedLinear F $.
\end{notation}

A remarkable feature of the $\Sol$ space is that it carries a naturally defined pre-symplectic form $\Omega$.
	It is "natural" modulo the fact that $\Sol$ is determined only once a Lagrangian or Hamiltonian has been chosen.
\\
 Therefore, $\Sol$ is the natural candidate for the field-theoretic (covariant) phase space.

@@

Since $\Conf$ and $\Sol$ are in general not linear, we have to regard them as manifolds.
Hence, we have to conveniently specify the structure of their tangent space in order to make the previous claim clear.

The first thing to point out is the following chain of inclusions:
\begin{displaymath}
	\Gamma^\infty_c\left(\phi^*(VF)\right) \; \subseteq \; T_\phi\Sol \; \subset \; T_\phi\Conf \; \subseteq \; \Gamma^\infty\left( \phi^\ast (VF) \right)
\end{displaymath}
%
This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
Therefore, a parametrized regular curve has to be regarded as a family of diffeomorphisms, the flow generated by a vertical tangent field on $F$.\\
To consider the pull-back bundles stresses the fact that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$, that are vertical fields of $F$ \underline{along} the section $\phi$.
\begin{notation}
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			 & Lagrangian picture & Hamiltonian picture \\
			\hline
			$\delta \phi \in T_\phi \Conf$		&	$\delta \varphi$		&	$(\delta \varphi, \delta \pi)$ \\
			\hline
		\end{tabular}
	\end{center}
\end{notation}

According to this interpretation, $T_\phi\Sol$ should consists of the generators of those variations that maps, at least infinitesimally, a solution $\phi\in\Sol$ in another solution.\\
In other words, it consists of the solutions of the \emph{Jacobi equations}.
Rigourosly, this can be expressed via the following definition:
	\begin{definition}[Tangent space to the Space of Solutions on a solution $\phi \in \Sol$]\label{Def:TangentSol}
		It is the vector space
		\begin{displaymath}
			T_\phi \Sol \coloneqq \ker(J[\phi]_\cdot)
		\end{displaymath}
		where $J$ is the so-called \emph{Jacobi Operator}.
	\end{definition}

\section{Jacobi Operator}\label{Sec:JacobiOperator}
Intuitively, the Jacobi equations are the formal linearization of the equation of motion around a solution $\phi$.\\
Everything can be encoded in the following operator:
%
	\begin{definition}[Jacobi operator pertaining to $D$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp} is the bundle map over $F$:
		\begin{displaymath}
			J(\phi) \; : \; \phi^\ast(VF) \rightarrow	\phi^\ast(V^\TwistedLinear F) 
			\quad s.t. \quad  \left(J(\phi)\right) V
			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda](x) \right\rvert_{\lambda=0} \right)
		\end{displaymath}
		where $V\in (\phi^\ast(VF))_{\phi(x)} = V_{\phi(x)}F$ and $\phi_\lambda$ is a regular variation generated by a $\delta\phi$ such that $\delta\phi_x = V$ and
		$\sigma$ is the canonical bundle-morphism \footnote{see \ref{Section:sigma} for further details.}
		\begin{displaymath}
			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
		\end{displaymath}
		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
		 and $0$ is the zero-section of $W$ over $F$.
	\end{definition}
	%
	\begin{remark}
		Being $J$ a bundle morphism, it can be naturally interpreted functionally as
		\begin{displaymath}
			\left(J(\phi)\right) [\: ] : 
			\Gamma^\infty\left(\phi^\ast(VF)\right) \rightarrow	
			\Gamma^\infty \left( 
			\phi^\ast(V^\TwistedLinear F)
			\right)
		\end{displaymath}
	\end{remark}
%
  \begin{minipage}[r]{0.5\textwidth}
    \includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
  \end{minipage}\hfill
  \begin{minipage}[l]{0.5\textwidth}
	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ mapt to the same space.
  \end{minipage}

@@

\begin{displaymath}
	\left( V_M W \right)_{0(e)} = 
	i\left[ V_E W \right]_{0(e)} \oplus \left( T_e 0 \left[ V_e E\right] \right)
\end{displaymath}
which determines an intrinsic mapping 
\begin{displaymath}
	\sigma_e : \left( V_M W \right)_{0(e)} \rightarrow \left( V_E W \right)_{0(e)} \simeq W_e
\end{displaymath}
that is simply the projection on the first component.

Since this projection is defined for all $e \in E$ and it acts fiberwise, it can be regarded as a bundle morphism over $E$:
\begin{displaymath}
	\sigma : 0^\ast \left( V_M W \right) \rightarrow 0^\ast \left( V_E W \right) \simeq W
\end{displaymath} 
Visually this is a map which "verticalize" w.r.t. $E$ the vertical vectors w.r.t. $M$ along $0(E) \subset W$.
%

\begin{minipage}{.5\textwidth}
  \centering
	\includestandalone[width=0.85\linewidth]{Pictures/Figure_sigmaAction}
 \\ \small{general case}
\end{minipage}
\begin{minipage}{.5\textwidth}
  \centering
	\includestandalone[width=0.85\linewidth, mode=buildnew]{Pictures/Figure_sigmaJacobi}
 \\ \small{ (Jacobi field variation)}
\end{minipage}%

\newpage
\section{Covariant approach: pre-symplectic form}
 Roughly, the strategy of construction is the following:

	\begin{center}
		\includestandalone[width=0.80\linewidth]{Pictures/Figure_symformidea}
	\end{center}
%
	\begin{itemize}
		\item Consider $\phi \in \Conf$ and 
		a pair of variations $\delta \phi_1 , \delta \phi_2 \in T_\phi \Conf$.
		\item Find a way to contract $\delta \phi$ and $\delta \phi '$ , seen as tangent vector field on $E$, with the multi-symplectic forms $\omega$.
		\item Pull-back the obtained $m-1$ form to $M$, oriented manifold.
		\item Integrate thus form on a suitable $(m-1)$ dimensional sub-manifold of $M$.
		\item Take the resulting number as the evaluation of the desired form on the two variations.  
	\end{itemize}
